$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-09-22 paper/paper.tex
Clarify Ciccone and Padovani's work

In their recent paper, Ciccone and Padovani mechanise a dependently-typed linear \picalc{} in Agda \cite{Ciccone}.
They do so by leveraging Agda's dependent types to provide a dependently-typed interpretation of messages.
Contexts contain not only types, but also the messages that inhabit their corresponding interpretation in Agda.
To avoid linearity violations, the interpretation of channel types is erased --- they are only present in the context of the typing judgment.
They model message input as a dependent function abstraction in Agda, and as a result are able to encode message predicates, branching, and variable-length conversations.
They use the concrete set of multiplicities $0$, $1$, $\omega$, define a partial algebra on contexts and require user-provided proofs of context split.

>>>>

In their recent paper, Ciccone and Padovani mechanise a dependently-typed linear \picalc{} in Agda \cite{Ciccone}.
Their intrinsic encoding allows them to leverage Agda's dependent types to provide a dependently-typed interpretation of messages --- to avoid linearity violations the interpretation of channel types is erased.
Message input is modeled as a dependent function in Agda, and as a result message predicates, branching, and variable-length conversations can be encoded.
In contrast to our work, their algebra is on the multiplicities $0$, $1$, $\omega$, and top-down context splitting proofs must be provided.
